Sequential rank agreement methods for comparison of ranked lists

### 2015-05-29 latex/paper.Rnw
Small fix

\documentclass[12pt,a4paper]{statsoc}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

@@

\section{Benchmarks}

@@

\section{Alternatives}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

@@

%%% RSS specific items

@@

\section{Evaluating sequential rank agreement}

@@

\section{Comparison to ...}

The overlap among $L$ lists observed until depth $d$ is defined as the
proportion of items that are found in all $L$ lists compared to the
possible number of items found in all lists observed until depth $d$:
\begin{equation}
O(d) = \frac{| \cap_{l=1}^L \{\pi_l(r); r\leq d \} |}{d}.
\end{equation}
Typically, the overlap is only considered for pairwise comparisons

The average overlap at depth $d$ is defined as the average of the
overlaps until $d$,
\begin{equation}
AO(d) = \sum_{i=1}^d \frac{O(d)}{d}.
\end{equation}
This definition indirectly ensures that extra emphasis is included on
the top of the list since the items
